### 2023-04-20 Rmd/Metadata overview.Rmd

  filter(nssbset > 0)

@@

d2 %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", nblim:ncatch) %>% 
  filter(data > 0) %>% 
  mutate(
    variable = factor(variable,
                      levels =c("nblim","nfmsy","nadvicelandings","nadvicecatch", "nfset", "nssbset",
                                "ntal","ntac","nlandings","ncatch"))
  ) %>%

>>>>

  filter(nssbset > 0 | nfset > 0 )

# writexl::write_xlsx(d1, "meta.xlsx")

@@

d2 %>% 
  mutate(
    stockkeylabelold = case_when(
      stockkeylabelold == "cod-nsea" ~ "cod-347d",
      stockkeylabelold == "ple-nsea2" ~ "ple-nsea",
      TRUE                            ~ stockkeylabelold
    ) 
  ) %>% 
  tidyr::pivot_longer(names_to = "variable", values_to = "data", nblim:ncatch) %>% 
  filter(data > 0) %>% 
  mutate(
    variable = factor(variable,
                      levels =c("nblim","nfmsy","nadvicelandings","nadvicecatch", "nfset", "nssbset",
                                "ntal","ntac","nlandings","ncatch"))
  ) %>%

### 2023-04-20 Rmd/Paper 03 short term forecast analysis.Rmd

# Load dataset
load(file=paste(dropboxdir, "/rdata/iAssess.RData",sep=""))
load(file=paste(dropboxdir, "/rdata/iAdvice.RData",sep=""))

@@

s   <- "sol-nsea"

>>>>

# Load dataset
iAssess <-
  loadRData(file=paste(dropboxdir, "/rdata/iAssess.RData",sep="")) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold=="ple-nsea2", "ple-nsea", stockkeylabelold))

iAdvice <-
  loadRData(file=paste(dropboxdir, "/rdata/iAdvice.RData",sep="")) %>% 
  mutate(stockkeylabelold = ifelse(stockkeylabelold=="ple-nsea2", "ple-nsea", stockkeylabelold))

@@

s   <- "ple-nsea"
